GSE158422: DNA methylation in Lung squamous cell carcinoma

### 2023-12-21 figs/GSE158422.Rmd
fix plots

if (sig > 10) {
  dmr <- run_dmrcate(mx=mxs,design=design)
  head(dmr)
  comp <- compartment_enrichment(dma)
  comp
  cgi <- cgi_enrichment(dma)
  cgi
} else {
  dmr <- NULL
  comp <- NULL
  cgi <- NULL
}
#make_dm_plots(dm = dm ,name=name , mx=beta,mxs=mxs, groups = groups,
  confects=confects,dmr = dmr, comp=comp, cgi=cgi)

>>>>

if (sig > 10) {
  dmr <- run_dmrcate(mx=mxs,design=design)
  head(dmr)
  comp <- compartment_enrichment(dma)
  comp
  cgi <- cgi_enrichment(dma)
  cgi
} else {
  dmr <- NULL
  comp <- NULL
  cgi <- NULL
}

make_dm_plots(dm = dm ,name=name , mx=beta,mxs=mxs, groups = groups,
  confects=confects,dmr = dmr, comp=comp, cgi=cgi)
